Maragra update: December 2018

### 2020-06-20 inst/rmd/nov2018/nov2018.Rmd
updated

---
title: "Final analysis for paper"
date: ''
fig_height: 2.6
output:
  pdf_document:
    includes:
      in_header: preamble.sty
    keep_tex: yes
    latex_engine: xelatex
  html_document:
    df_print: paged
fig_width: 4
always_allow_html: true
subtitle: Brew, Pradhan, Sicuri
bibliography: bibliography.bib
---

@@

# Packages
library(tidyverse)
library(knitr)
library(Hmisc)
library(brew)
library(maragra)
library(RColorBrewer)
library(extrafont)
library(kableExtra)
library(raster)
loadfonts()
## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               fig.height = 4,
               fig.width = 5,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               # dev = "cairo_pdf",
               fig.pos="!h",
               fig.align = 'center')
knitr::opts_chunk$set(error = FALSE)

opts_knit$set(width=75)
options(xtable.comment = FALSE)
```

@@

# Calculate household protection

```{r}

# Manuscript draft

Draft of the paper \href{https://docs.google.com/document/d/1bUWRBCgVcgjSPHchIQxiTG8Vwv5hV1GLU4Tlu386sWA/edit#}{HERE}.

# Classify protection plot

```{r}
pd <- data_frame(days_since = 1:230)
pd$protection <- classify_protection(pd$days_since)

ggplot(data = pd,
       aes(x = days_since,
           y = protection)) +
  geom_area(fill = 'lightblue', alpha = 0.8,
            lwd = 0.2,
            color = 'black') +
  geom_vline(xintercept = 0,
             lty = 2, alpha = 0.6) +
  theme_maragra() +
  labs(x = 'Days since IRS application',
       y = 'Protection score')
```

@@

```{r}
desc <- final_data %>%
  group_by(permanent_or_temporary) %>%
  summarise(workers = length(unique(oracle_number)),
            days = n())
```

@@

```{r}
pq <- sort(unique(final_data$protection))
# pq <- quantile(final_data$protection,
#                seq(0, 1, 0.1))
# pq <- sort(unique(pq))
x <- final_data %>%
  # mutate(protection_cat = protection_var) %>%
  mutate(protection_cat = ifelse(protection <= pq[2],
                                 'Protection 1',
                                 ifelse(protection <= pq[3],
                                        'Protection 2',
                                        ifelse(protection <= pq[4],
                                               'Protection 3',
                                               ifelse(protection <= (pq[5] + 0.1),
                                                      'Protection 4',
                                                      NA))))) %>%
  group_by(protection_cat) %>%
  summarise(ab_rate = length(which(absent))/ n() * 100)

@@

```{r}
ggplot(data = x,
       aes(x = `Quantile`,
           y = `Absenteeism rate`)) +
  geom_bar(stat = 'identity',
           alpha = 0.8,
           color = 'black',
           lwd = 0.2,
           fill = 'lightblue') +
  labs(x = 'Protection score quantile') +
  facet_wrap(~Group) +
  theme_maragra()
```

@@

```{r}
# Combined protection
summary(final_model)

@@

```{r}
# on <- sort(unique(final_data$oracle_number))
fake <- expand.grid(#group = sort(unique(monthly$group)),
  rain_var = rq,
  protection_var = pq)#,
fake$predicted <- NA #fake$predicted_upr <- fake$predicted_lwr<- NA

fe <- getfe(final_model)
# # fake <- left_join(fake, fe %>% dplyr::select(idx, effect, obs), 
# #                                              by = c('oracle_number'= 'idx'))
predictions <- exp(predict(final_model_lm, fake, interval = 'confidence'))-1
# predictions <- data.frame(predictions)
# # # Add the fixed effects
fixed_effects <- fe$effect
# 
fake$predicted<- predictions[,1]
fake$predicted_upr <- predictions[,3]
fake$predicted_lwr <- predictions[,2]
# 
# # # Add fixed effects
# # fake <- fake %>%
# #   mutate(predicted = predicted + effect,
# #          predicted_upr = predicted_upr + effect,
# #          predicted_lwr = predicted_lwr + effect)
# 
# pd <- fake %>%
#   filter(protection_var == pq[1]) 
# ggplot(data = pd,
#        aes(x = rain_var,
#            y = predicted)) +
#   geom_point()

@@

```{r, eval = FALSE}
g1 <- ggplot(data = fake %>% filter(protection_var == pq[1]),
       aes(x = rain_var,
           y = predicted)) +
  geom_point() +
  geom_line() +
  geom_ribbon(aes(ymin = predicted_lwr,
                  ymax = predicted_upr),
              alpha = 0.4,
              fill = 'darkorange') +
  labs(y = 'Predicted absenteeism rate',
       x = '1-3 month precipitation lag',
       title = 'Lagged precipitation and absenteeism') +
  theme_maragra()

g2 <- ggplot(data = fake %>% filter(rain_var == rq[1]),
       aes(x = protection_var,
           y = predicted)) +
  geom_point() +
  geom_line() +
  geom_ribbon(aes(ymin = predicted_lwr,
                  ymax = predicted_upr),
              alpha = 0.4,
              fill = 'darkorange') +
  labs(y = 'Predicted absenteeism rate',
       x = 'Protection index',
       title = 'IRS-afforded protection and absenteeism') +
  theme_maragra()

Rmisc::multiplot(g1, g2, cols = 2)
```

@@

# combine other info
predictions <- predictions %>% bind_cols(sim_data %>% dplyr::select(date, absent, strategy, permanent_or_temporary)) %>%
  mutate(absent = as.numeric(absent)) %>%
  filter(!is.na(fit))

@@

zero <- predictions %>%
  filter(strategy == 'Zero') %>%
  mutate(year = as.numeric(format(date, '%Y'))) %>%
  group_by(year) %>%
  summarise(n = n(),
            actual_absences = sum(absent),
            predicted_absences = sum(fit, na.rm = TRUE),
            actual = mean(absent, na.rm = TRUE),
            predicted = mean(fit, na.rm = TRUE)) %>%
  mutate(avoided = predicted_absences - actual_absences)
  # dplyr::rename(value = predicted) %>%
  # dplyr::select(permanent_or_temporary, value, predicted_absences)

kable(simple)

# Eligible working days
sum(zero$n)
# Absences
sum(zero$actual_absences)
# Actual absence rate
sum(zero$actual_absences) / sum(zero$n)
# Would have observed
sum(zero$predicted_absences)
# Predicted - observ
sum(zero$predicted_absences) - sum(zero$actual_absences)
# Overall reduction from
sum(zero$predicted_absences) / sum(zero$n)
# To
sum(zero$actual_absences) / sum(zero$n)
# Number of working days permanent vs temp
table(predictions$permanent_or_temporary[predictions$strategy=='Real'])
# Absences avoided among permanent workers
predictions %>% filter(strategy == 'Zero') %>% group_by(permanent_or_temporary) %>% summarise(n = n(),
            actual_absences = sum(absent),
            predicted_absences = sum(fit, na.rm = TRUE),
            actual = mean(absent, na.rm = TRUE),
            predicted = mean(fit, na.rm = TRUE)) %>%
  mutate(avoided = predicted_absences - actual_absences) %>%
  # decline due to irs
  mutate(decline = predicted - actual)
# One absence every n days
sum(zero$n) / sum(zero$avoided)
# Annual reduction in absence
mean(zero$avoided[zero$year < 2016])
# Cost per absence avoided
68984 / 4183
# Percentage of absence among permanent workers
x = predictions %>%
  filter(strategy == 'Zero') %>%
  # filter(date < '2016-01-01') %>%
  group_by(permanent_or_temporary) %>%
  summarise(absences = sum(absent),
            predicted = sum(fit)) %>%
  mutate(averted = predicted - absences) %>%
  mutate(p = averted / sum(averted))
x
# Weighted average cost
y = sum(c(25, 5) * x$p)
y
# Cost of treatment per absence
22 / 80
# Total savings per aversion
0.275 + y
# Total yearly savings
(0.275 + y) * 4183
# Total yearly savings
((0.275 + y) * 4183) - 68984
# ROI
((0.275 + y) * 4183) / 68984
# Additional max strategy
simple
47943-42131
```

@@

```{r}
# paste0(
#   "Of the ", nrow(simulations[simulations$strategy == 'Real',]),
#   " eligible working days in our panel, we observed ", nrow(simulations[simulations$strategy == 'Real' & simulations$absent,]), 
#   " absences. Using the above approach, we estimate that we would have observed ",
#   length(which(simulations$absent[simulations$strategy == 'Zero'])),
#   " had it not been for the firm's IRS program, for a total of ",
#   length(which(simulations$absent[simulations$strategy == 'Zero'])) - length(which(simulations$absent[simulations$strategy == 'Real'])),
#   " avoided absences. This translates to an overall reduction in absenteeism from ",
#   round(length(which(simulations$absent[simulations$strategy == 'Zero'])) / nrow(simulations %>% filter(strategy == 'Zero')) * 100, digits = 2),
#   "% (without its IRS program) to the observed ", round(length(which(final_data$absent)) / nrow(final_data) * 100, digits = 2),"%.
# The number of working-days observed among permanent workers (",
# length(which(final_data$permanent_or_temporary == 'Permanent')),") was nearly thrice that of those of temporary workers (", 
# length(which(final_data$permanent_or_temporary == 'Temporary')),
# ").") 
# 
# 
# 
# paste0(
#   "By the same token, the number of absences avoided among permanent workers (39,890) was far greater than that of temporary workers (8,972). The latter had a greater relative decline in absenteeism due to IRS (from 9.3% to 3.91%) relative to the former (from 14.2% to 11%), but the aggregate numbers are less consequential since (a) temporary workers have a lower baseline absenteeism rate and (b) they work, by definition, fewer days. In total, the IRS program is estimated to prevent one absence every 26.6 working days.
# Annually, this translates to approximately 4,076 avoided absences per year (slightly greater than the simple splicing of the overall figure into the 4-year study period, since we did not have complete data for all worker types).
# "
# )
```

```{r}
ggplot(data = simple,
       aes(x = strategy,
           y = predicted_absences)) +
  geom_bar(stat = 'identity',
           alpha = 0.6,
           color = 'black') +
  labs(y = 'Absenteeism rate',
       x = 'Strategy') +
  geom_label(aes(label = round(predicted_absences, digits = 3)),
             nudge_y = -10000)
```

@@

```{r, eval = FALSE}
x <- final_data %>%
  left_join(irs %>% dplyr::select(date, unidade, days_since))

@@

# Charts for paper

```{r, results='asis'}
# x <- ab_panel %>%
#   left_join(workers %>%
#               dplyr::select(oracle_number, date_of_birth, permanent_or_temporary, sex))
x <- final_data
x <- x %>% left_join(workers %>% dplyr::select(oracle_number, date_of_birth))
x$age <-as.numeric(as.Date('2014-01-01') - x$date_of_birth) / 365.25
x$agey <- x$age
x$age <- round(x$age, digits = -1)
x$status <- x$permanent_or_temporary

calculate <- function(var= 'sex',
                      data){
  out <- 
    data %>%
    group_by_(var) %>%
    summarise(`Number of workers` = length(unique(oracle_number)),
              `Number of days observed` = n()) %>%
    # summarise(`Treatment workers` = length(unique(oracle_number[!months_since %in% c('Never', 'Before')])),
    #           `Treatment days` = length(oracle_number[!months_since %in% c('Never', 'Before')]),
    #           `Control workers` = length(unique(oracle_number[months_since %in% c('Never', 'Before')])),
    #           `Control days` = length(oracle_number[months_since %in% c('Never', 'Before')])) %>%
    ungroup() %>%
    # mutate(p = round(n / sum(n) * 100, digits = 2)) %>%
    mutate(variable = '') 
    names(out)[1] <- ' '
    out$variable[1] <- Hmisc::capitalize(var)

    out <- out %>% dplyr::select(variable, ` `, 
                                 `Number of workers`, `Number of days observed`)
                                 # `Treatment workers`, `Treatment days`, `Control workers`, `Control days`)
    out$` ` <- as.character(out$` `)
  return(out)
}
out_list <- list()
vars <- c('department', 
           'sex',
           'status',
           'age')
for(i in 1:length(vars)){
  message(i)
  y <- calculate(var = vars[i], data = x)
  out_list[[i]] <- y
}
demo_table <- bind_rows(out_list)
names(demo_table)[1:2] <- c('Variable', ' ')
kable(demo_table, format = 'html') %>% kable_styling()
# print(xtable::xtable(demo_table,
#                      caption = 'Overall worker characteristics',
#                      align = c('r', 'r', rep('l', 5))),
#       include.rownames = FALSE)

```{r, fig.width = 6, fig.height = 3.5, fig.align='center', fig.cap = 'i. Monthly total precipitation in the Maniça district; ii. Average monthly temperature (bars) during the study period, as well as monthly maximum (red) and minimum (blue) temperatures'}
x <- weather %>%
  mutate(month = format(date, '%m')) %>%
  mutate(year = format(date, '%Y')) %>%
  mutate(date = as.Date(paste0(year, '-', month, '-01'))) %>%
  group_by(date) %>%
  summarise(precipitation = sum(precipitation, na.rm = TRUE),
            temp_max = max(temp_max, na.rm = TRUE),
            temp_min = min(temp_min, na.rm = TRUE),
            temp = mean(temp))
# x <- gather(x, key, value,precipitation:temp)

g1 <- ggplot(data = x,
       aes(x = date,
           y = precipitation)) +
  geom_bar(stat = 'identity',
           fill = 'lightblue',
           size = 0.1) +
  theme_maragra() +
  theme(axis.text.x = element_text(angle = 0)) +
  labs(x = 'Month',
       y = 'Milimeters',
       title = 'A. Monthly precipitation') +
  scale_x_date(labels = scales::date_format("%Y"))

g2 <- ggplot(data = x,
            aes(x = date,
                y = temp)) +
  # geom_bar(stat = 'identity', fill = 'grey', size = 0.1) +
  geom_line(aes(y = temp_max),
             color = 'darkred', 
             alpha = 0.5) +
  geom_line(aes(y = temp_min),
             color = 'blue', 
             alpha = 0.5) +
  # geom_linerange(aes(ymin = temp_min,
  #                    ymax = temp_max),
  #                alpha = 0.6,
  #                color = 'blue') +
   theme_maragra() +
  theme(axis.text.x = element_text(angle = 0)) +
  labs(x = 'Month',
       y = 'Degrees (Celcius)',
       title = 'B. Monthly temperature') +
  scale_x_date(labels = scales::date_format("%Y"))
Rmisc::multiplot(g1, g2, cols = 2)
```

```{r, fig.cap = 'Clinical malaria (district of Manhiça), all-cause absenteeism among Maragra workers, sick absenteeism among Maragra workers, positive cases at company clinic, and test positivity rate at company clinic', fig.height=5, fig.width=8}
# BES incidence
g1 <- 
  ggplot(data = bes %>%
           mutate(season = ifelse(p >= median(p), 'High season',
                                  'Low season')) %>%
           filter(weekdays(date) == 'Monday',
                  date <= '2016-12-01'),
       aes(x = date,
           y = p)) +
  geom_point(alpha = 0.6,
             aes(color = season),
             size = 0.2) +
  geom_line(alpha = 0.1) +
  theme_maragra(base_size = 9) +
  labs(x = 'Date',
       y = 'Incidence',
       title = 'A: Annualized district clinical\nmalaria incidence per 1,000') +
  scale_color_manual(name = '',
                     values = c('red', 'black')) + 
  guides(color = guide_legend(ncol = 1)) +
  theme(legend.position = c(.8, .8),
        legend.text = element_text(size = 5),
        legend.background = element_rect(fill=alpha('white', 0))) +
  theme(axis.title.x = element_blank())

# Absenteeism rate
g2_data <- final_data %>%
  # filter(date <= '2016-12-01') %>%
  group_by(month = as.Date(paste0(format(date, '%Y-%m'), '-01')), permanent_or_temporary) %>%
  summarise(absences = length(which(absent)),
            # absences_sick = length(which(absent_sick)),

            eligibles = n()) %>%
  mutate(absenteeism_rate = absences / eligibles * 100)

g2 <- ggplot(data = g2_data,
             aes(x = month,
                 y = absenteeism_rate,
                 lty = permanent_or_temporary)) +
  geom_line(alpha = 0.6) +
  theme_maragra(base_size = 9) +
  labs(x = 'Date',
       y = 'Absenteeism rate',
       title = 'B: Monthly absenteeism rate') +
  scale_linetype_manual(name = '', values = c(1,4)) +
  theme(legend.position = c(.84, .8)) +
  guides(lty = guide_legend(ncol = 1)) +
    theme(axis.title.x = element_blank())

# Weather
g4 <-
  ggplot(data = weather %>%
           group_by(date = as.Date(paste0(format(date, '%Y-%m'), '-01'))) %>%
           summarise(precipitation = sum(precipitation, na.rm = TRUE)),
         aes(x = date,
             y = precipitation)) +
  geom_line(alpha = 0.6) +
  theme_maragra(base_size = 9) +
  labs(x = 'Date',
       y = 'Mililiters',
       title = 'D: Monthly precipitation') +  theme(axis.title.x = element_blank())

# Clinical incidence of malaria
g5 <- clinic_agg %>%
  filter(date >= '2013-01-01', date <= '2016-12-31') %>%
  # mutate(date = as.Date(paste0(year, '-', month, '-01'))) %>%
  group_by(date) %>%
  summarise(tested = sum(tested),
            positive = sum(positive)) %>%
  ungroup %>%
  mutate(percent_positive = positive / tested * 100) %>%
  ggplot(aes(x = date,
             y = positive)) +
  geom_line(alpha = 0.6) +
  theme_maragra(base_size = 9) +
  labs(x = 'Date',
       y = 'Cases',
       title = 'C: Monthly malaria cases\nat company clinic') +
    theme(axis.title.x = element_blank())

g6 <- clinic_agg %>%
  filter(date >= '2013-01-01', date <= '2016-12-31') %>%
  # mutate(date = as.Date(paste0(year, '-', month, '-01'))) %>%
  group_by(date) %>%
  summarise(tested = sum(tested),
            positive = sum(positive)) %>%
  ungroup %>%
  mutate(percent_positive = positive / tested * 100) %>%
  ggplot(aes(x = date,
             y = percent_positive)) +
  geom_line(alpha = 0.6) +
  theme_maragra(base_size = 9) +
  labs(x = 'Date',
       y = 'Cases',
       title = 'D: Monthly malaria test positivity rate\nat company clinic') +
    theme(axis.title.x = element_blank())

# Rmisc::multiplot(g1, g2, g3,
#                  # g4, 
#                  g5, g6, layout = matrix(c(1, 1, 2, 3, 4, 5), nrow=2, byrow=TRUE)) 
Rmisc::multiplot(g1,  g5,g2, g6, cols = 2)
```

```{r}
fumigations <- mc %>%
  filter(date >= '2013-01-01',
         date <= '2016-12-31')
n_fumigations <- nrow(fumigations)
n_buildings <- sum(fumigations$casas_cobertas, na.rm = TRUE)
unique_agregados <- length(unique(fumigations$unidade))
people_sprayed <- length(unique(final_data$oracle_number[final_data$days_since != 'Never']))
people_observed <- length(unique(final_data$oracle_number))
pr <- function(x){prettyNum(x, big.mark = ',')}
```

**Fumigations**: During the period from January 1st, 2013 through December 31st, 2016, the Maragra Malaria Control Unit carried out `r pr(n_fumigations)` episodes of fumigation of residential "agregados" (household combinations), for a total of `r pr(n_buildings)` building-fumigation combinations. The total number of unique agregados sprayed during this period was `r pr(unique_agregados)`. Among the `r pr(people_observed)` workers for whom we have reliable absenteeism and residential data, `r pr(people_sprayed)` had their homes fumigated at least once (the majority of workers live off of the facility).

```{r}
dry_days <- length(which(weather$precipitation > 0))
n_days <- length(weather$precipitation)
p_dry <- round(dry_days / n_days * 100)
amount_rain <- round(mean(weather$precipitation[weather$precipitation > 0], na.rm = T), digits = 2)
x <- weather %>%
  group_by(month = format(date, '%m')) %>%
  summarise(precipitation = mean(precipitation, na.rm = TRUE))
```

**Absences**: We observed `r pr(nrow(ab_panel))` unique worker-days among the `r pr(people_observed)` workers. The all-period average absenteeism rate was `r round(100 * sum(ab_panel$absent) / nrow(ab_panel), digits = 2)`%, though this rate varied widely as a function of worker department, sex, residence, and season (table 1).

```{r, results='asis'}
calculate <- function(var){
  out <- 
  final_data %>%
    mutate(year = format(date, '%Y')) %>%
    # mutate(on_site = ifelse(on_site,
    #                                 # 'On site',
    #                                 # 'Off site'),
    #        rainy = ifelse(rainy,
    #                       'Rainy',
    #                       'Dry')) %>%
    # filter(!is.na(rainy)) %>%
  group_by_(var, 'year') %>%
  summarise(absences = length(which(absent)),
            eligibles = length(absent),
            workers = length(unique(oracle_number))) %>%
  ungroup %>%
  mutate(absenteeism_rate = absences / eligibles * 100) 
  names(out)[1] <- 'variable'
  out$val <- paste0(round(out$absenteeism_rate, digits = 1),
                    '%')#,
                    # ')',
                    # '\n',
                    # ' (workers:', out$workers,
                    # ')')
  out <- 
    out %>%
    dplyr::select(variable, year, val)

  out <- out %>%
    spread(key = year,
           value = val)
  out$variable <- as.character(out$variable)
  new_var <- #ifelse(var == 'on_site',
                    # 'Residence',
                    ifelse(var == 'rainy',
                           'Precipitation',
                           var)
  # )
  left <- data.frame(x = c(new_var, rep('', (nrow(out) - 1))))
  out <- cbind(left, out)
  names(out)[1:2] <- c('Variable', 'x')
  # out$variable[1] <- paste0(Hmisc::capitalize(new_var), ': ', out$variable[1])
  return(out)
}
out_list <- list()
vars <- c('field', 'permanent_or_temporary', 'sex')
# vars <- c(#'season', 
#            'field',
#           'permanent_or_temporary',
#            'sex')#,
#            # 'on_site',
#            # 'rainy'
#           # )
for(i in 1:length(vars)){
  x <- calculate(var = vars[i])
  out_list[[i]] <- x
}
ab_table <- bind_rows(out_list)
ab_table$Variable <- Hmisc::capitalize(ab_table$Variable)
# ab_table$Variable[ab_table$Variable == 'Season'] <- 'Malaria season'
ab_table$Variable[ab_table$Variable == 'Field'] <- 'Worker type'
ab_table$Variable[ab_table$Variable == 'Permanent_or_temporary'] <- 'Contract'
ab_table$x <- Hmisc::capitalize(ab_table$x)
names(ab_table)[2] <- ''
kable(ab_table, format = 'html') %>% kable_styling()
# print(xtable::xtable(ab_table,
#                      caption = 'Absenteeism rate by year and worker characteristics',
#                      align = c('r', 'r', 'l', rep('l', 4))),
#       include.rownames = FALSE)
```

```{r}
ov_ab <- round(100 * mean(ab_panel$absent[between(ab_panel$date, as.Date('2012-01-01'), as.Date('2016-12-31'))]), digits = 2)

ov_cl <- length(which(between(clinic$date, as.Date('2012-01-01'), as.Date('2016-12-31'))))
```

**Precipitation**: Of the `r n_days` days observed, `r dry_days` had no rainfall at all (ie, approximately two-thirds). On days for which there was any rainfall at all, the average amount was approximately `r amount_rain` centimeters. Rain was most common in December and January (average of 5-5.5 cm daily) and least common in August and September (average of 0.5 cm daily). Days with any rainfall saw more absenteeism than days with no rainfall (Figure 6, panel A) and among days with any rainfall, more precipitation was associated with greater absenteeism (Figure 6, panel B) (correlation coefficient of 0.25).

```{r, fig.cap = 'Rainfall and absenteeism: association of any rainfall with absenteeism rate (left) and association of rainfall amount and absenteeism (right)', fig.height=3.5, fig.width=7, fig.align='center'}
bi_data <- final_data %>%
  group_by(date) %>%
  mutate(any_rain = mean(precipitation, na.rm = TRUE) > 0) %>%
  ungroup %>%
  filter(!is.na(any_rain)) %>%
  mutate(any_rain = ifelse(any_rain, 'Some rain', 'No rain')) %>%
  group_by(any_rain, date) %>%
  summarise(absenteeism = mean(absent) * 100)
bi_data_simple <- bi_data %>%
  group_by(any_rain) %>%
  summarise(absenteeism = mean(absenteeism))
p1 <- ggplot(data = bi_data,
       aes(x = any_rain,
           y = absenteeism)) +
  geom_jitter(alpha = 0.3, size = 0.5) +
  geom_violin(alpha = 0.4, fill = 'lightblue') +
  scale_y_log10() +
  theme_maragra() +
  geom_point(data = bi_data_simple,
             aes(x = any_rain,
                 y = absenteeism),
             alpha = 0.8) +
  geom_text(data = bi_data_simple,
             aes(x = any_rain,
                 y = absenteeism,
                 label = paste0(round(absenteeism, digits = 2), '\n(median)')),
             color = 'black') +
  labs(x = '',
       y = 'Absenteeism rate (log scale)',
       title = 'A')

plot_data <- final_data %>%
  group_by(date) %>%
  summarise(precipitation = mean(precipitation, na.rm = TRUE),
            absenteeism = mean(absent)) %>%
  ungroup %>%
  filter(precipitation > 0.1)
p2 <- ggplot(data = plot_data,
       aes(x = precipitation,
           y = absenteeism * 100)) +
  geom_point(alpha = 0.3, size = 0.5) +
  scale_x_log10() +
  geom_smooth() +
  # scale_y_log10() +
  theme_maragra() +
  labs(x = 'Daily precipitation (log scale)',
       y = 'Absenteeism rate', 
       title = 'B')
Rmisc::multiplot(p1, p2, cols = 2)
```

```{r, fig.align = 'center', fig.cap = 'Distribution of herd protection score in panel data', eval = F}
pd <- final_data %>%
  group_by(protection) %>% tally
ggplot(data = pd,
       aes(x = protection,
           y = n)) +
  geom_bar(stat = 'identity',
           fill = 'lightblue',
               alpha = 0.6) +
  theme_maragra() +
  labs(x = 'Herd protection score',
       y = 'Density')
```

## Sensitivity analysis

```{r, eval = FALSE}

# The below shows average FE for year / worker, during malaria season, on a rainy day...

expander <- function(x){sort(unique(unlist(final_data[,x])))}
dummy <- expand.grid(#season = expander('season'),
                     months_since = expander('months_since'),
                     rainy_day = expander('rainy_day'),
                     herd = mean(final_data$herd),
                     group = expander('group'))
dummy$predicted <- NA

>>>>

---
title: "Maragra update: December 2018"
subtitle: "Brew, Pradhan, Sicuri"
date: ''
output: 
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: preamble.sty
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
---

@@

# Packages
library(tidyverse)
library(knitr)
library(Hmisc)
library(brew)
library(maragra)
library(RColorBrewer)
library(extrafont)
library(kableExtra)
library(raster)
loadfonts()
## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               fig.height = 4,
               fig.width = 5,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               dev = "cairo_pdf",
               fig.pos="!h",
               fig.align = 'center')
opts_knit$set(width=75)
options(xtable.comment = FALSE)
```

@@

\begin{center}
\begin{large}

Maragra models

\end{large}
\end{center}

\vspace{5mm}

\begin{center}
\textbf{Overview}  
\end{center}

\vspace{5mm}
\begin{center}
\begin{changemargin}{3cm}{3cm}

This document contains an overview of the modeling approach and simulations results.

\end{changemargin}
\end{center}

\vspace{20mm}

\noindent\fbox{%
    \parbox{\textwidth}{%
        \subsection*{Main points}
        \begin{itemize}
          \item We have a new modeling approach
          \item We have carried out basic simulations for several malaria control strategies
          \item Results are consistent/coherent
          \item We have not yet implemented geographical variation
        \end{itemize}
        \vspace{2mm}
    }%
}

\vfill
\null

\subsection*{Desinataires}
\textbf{Elisa Sicuri; Menno Pradhan}

\vspace{3mm}

# Current paper

Draft of the paper (\href{https://docs.google.com/document/d/1bUWRBCgVcgjSPHchIQxiTG8Vwv5hV1GLU4Tlu386sWA/edit#}{HERE}

# Code

In R, our model looks like this

```{r, echo = FALSE}
final_model$call
```

Where `protection` is the sum of all nearby IRS, weighted by the inverse of the distance from the residence of the person (including the person's own residence).

# Reproduction of charts

## Number of workers by department

```{r}
plot_data <- ab_panel %>%
  left_join(workers %>% dplyr::select(oracle_number,
                                      department,
                                      permanent_or_temporary)) %>%
  mutate(year_month = as.Date(paste0(format(date, '%Y-%m'), '-01'))) %>%
  mutate(group = department) %>%
  # mutate(field = ifelse(department == 'Field', 
  #                            'Field worker',
  #                            'Not field worker')) %>%
  # mutate(group = paste0(permanent_or_temporary, ' ',
  #                         tolower(field))) %>%
  group_by(group, year_month) %>%
  summarise(n = length(unique(oracle_number)))

ggplot(data = plot_data,
       aes(x = year_month,
           y = n,
           color = group)) +
  geom_line()
```

## Number of temporary workers over time

```{r}
plot_data <- ab_panel %>%
  left_join(workers %>% dplyr::select(oracle_number,
                                      department,
                                      permanent_or_temporary)) %>%
  mutate(year_month = as.Date(paste0(format(date, '%Y-%m'), '-01'))) %>%
  # mutate(group = department) %>%
  mutate(group = ifelse(department == 'Field',
                             'Field worker',
                             'Not field worker')) %>%
  # mutate(group = paste0(permanent_or_temporary, ' ',
  #                         tolower(field))) %>%
  group_by(group, year_month) %>%
  summarise(n = length(unique(oracle_number)))

ggplot(data = plot_data,
       aes(x = year_month,
           y = n,
           color = group)) +
  geom_line()
```

## Absenteeism rate over time

```{r}
plot_data <- ab_panel %>%
  left_join(workers %>% dplyr::select(oracle_number,
                                      department,
                                      permanent_or_temporary)) %>%
  mutate(year_month = as.Date(paste0(format(date, '%Y-%m'), '-01'))) %>%
  mutate(group = department) %>%
  # mutate(group = ifelse(department == 'Field',
  #                            'Field worker',
  #                            'Not field worker')) %>%
  # mutate(group = paste0(permanent_or_temporary, ' ',
  #                         tolower(field))) %>%
  group_by(group, year_month) %>%
  summarise(abs = length(which(absent)),
            eligibles = n()) %>%
  mutate(ab_rate = abs / eligibles * 100)

ggplot(data = plot_data,
       aes(x = year_month,
           y = ab_rate,
           color = group)) +
  geom_line()
```

## Absenteeism rate over time by worker type

```{r}
plot_data <- ab_panel %>%
  left_join(workers %>% dplyr::select(oracle_number,
                                      department,
                                      permanent_or_temporary)) %>%
  mutate(year_month = as.Date(paste0(format(date, '%Y-%m'), '-01'))) %>%
  # mutate(group = department) %>%
  mutate(field = ifelse(department == 'Field',
                             'Field worker',
                             'Not field worker')) %>%
  mutate(group = paste0(permanent_or_temporary, ' ',
                          tolower(field))) %>%
  group_by(group, year_month) %>%
  summarise(abs = length(which(absent)),
            eligibles = n()) %>%
  mutate(ab_rate = abs / eligibles * 100)

ggplot(data = plot_data,
       aes(x = year_month,
           y = ab_rate,
           color = group)) +
  geom_line()
```

## Number of workers over time by worker type

```{r}
plot_data <- ab_panel %>%
  left_join(workers %>% dplyr::select(oracle_number,
                                      department,
                                      permanent_or_temporary)) %>%
  mutate(year_month = as.Date(paste0(format(date, '%Y-%m'), '-01'))) %>%
  # mutate(group = department) %>%
  mutate(field = ifelse(department == 'Field',
                             'Field worker',
                             'Not field worker')) %>%
  mutate(group = paste0(permanent_or_temporary, ' ',
                          tolower(field))) %>%
  group_by(group, year_month) %>%
  summarise(n = length(unique(oracle_number)))

ggplot(data = plot_data,
       aes(x = year_month,
           y = n,
           color = group)) +
  geom_line()
```

@@

@@

```{r}
pq <- quantile(final_data$protection,
               seq(0, 1, 0.1))
pq <- sort(unique(pq))
x <- final_data %>%
  # mutate(protection_cat = protection_var) %>%
  mutate(protection_cat = ifelse(protection <= pq[2],
                                 'Protection 1',
                                 ifelse(protection <= pq[3],
                                        'Protection 2',
                                        ifelse(protection <= pq[4],
                                               'Protection 3',
                                               ifelse(protection <= (pq[5] + 0.1),
                                                      'Protection 4',
                                                      NA))))) %>%
  group_by(protection_cat) %>%
  summarise(ab_rate = length(which(absent))/ n() * 100)

@@

```{r}
ggplot(data = x,
       aes(x = `Quantile`,
           y = `Absenteeism rate`)) +
  geom_bar(stat = 'identity',
           alpha = 0.6,
           color = 'black') +
  labs(x = 'Protection score quantile') +
  facet_wrap(~Group)
```

@@

```{r}
summary(final_model)
```

@@

```{r}
fake <- expand.grid(#group = sort(unique(monthly$group)),
  rain_var = rq,
  protection_var = pq)#,
fake$predicted <- fake$predicted_upr <- fake$predicted_lwr<- NA

fe <- getfe(final_model)
predictions <- exp(predict(final_model_lm, fake, interval = 'confidence'))-1
# predictions <- data.frame(predictions)
# # Add the fixed effects
# fixed_effects <- fe$effect

fake$predicted<- predictions[,1]
fake$predicted_upr <- predictions[,3]
fake$predicted_lwr <- predictions[,2]
```

@@

```{r}
ggplot(data = fake %>% filter(protection_var == pq[1]),
       aes(x = rain_var,
           y = predicted)) +
  geom_point() +
  geom_line() +
  geom_ribbon(aes(ymin = predicted_lwr,
                  ymax = predicted_upr),
              alpha = 0.4,
              fill = 'darkorange') +
  labs(y = 'Predicted absenteeism rate',
       x = '1-3 month precipitation lag',
       title = 'Lagged precipitation and absenteeism')
```

### IRS protection's effect

```{r}
ggplot(data = fake %>% filter(rain_var == rq[1]),
       aes(x = protection_var,
           y = predicted)) +
  geom_point() +
  geom_line() +
  geom_ribbon(aes(ymin = predicted_lwr,
                  ymax = predicted_upr),
              alpha = 0.4,
              fill = 'darkorange') +
  labs(y = 'Predicted absenteeism rate',
       x = 'Protection index',
       title = 'IRS-afforded protection and absenteeism')
```

@@

# combine other info
predictions <- predictions %>% bind_cols(sim_data %>% dplyr::select(date, absent, strategy)) %>%
  mutate(absent = as.numeric(absent)) %>%
  filter(!is.na(fit))

@@

kable(simple)
```

@@

```{r}
ggplot(data = simple,
       aes(x = strategy,
           y = predicted_absences)) +
  geom_bar(stat = 'identity',
           alpha = 0.6,
           color = 'black') +
  labs(y = 'Absenteeism rate',
       x = 'Strategy') 
```

@@

```{r}
x <- final_data %>%
  left_join(irs %>% dplyr::select(date, unidade, days_since))

@@
